Quantum Computation and Quantum Information\\ Assignment 3

### 2024-05-01 assignments/assignment-3.tex
adding assigment 3

\begin{mdframed}[backgroundcolor = gray!30,
  frametitle = Exercise 1.2]
  Explain how a device which, upon input of one of two non-orthogonal quantum states $\ket{\psi}$ and $\ket{\varphi}$ correctly identified the state, could be used to build a device which cloned the states $\ket{\psi}$ and $\ket{\varphi}$, in violation of the non-cloning theorem. Conversely, explain how a device for cloning could be used to distinguish non-orthogonal quantum states.
\end{mdframed}

>>>>

\begin{mdframed}[backgroundcolor = gray!30,
  frametitle = Exercise 4.30]
  Suppose $U$ is a single-qubit unitary operation. Find a circuit containing $\mathcal{O}(n^2)$ Toffoli, CNOT and single qubit gates which implements a $C^n (U)$ gate (for $n>3$), using no work qubits. 
\end{mdframed}
